\documentclass{tufte-handout}

\usepackage{style}

\begin{document}

%Question 10

\begin{question}

\qpart

Let \( k = \text{number of aliens} \) and \( n = \text{number of blue eared aliens} \).

Every blue eareed alien would leave on the \( n^{th} \) day at \( 6am \).

\qpart

If, say, \( k=2 \) and  \( n=1 \), then the blue eared alien would leave at \( 6am \) the next day, knowing
that they are the only one on the plantoid with blue ears.

If \( K=2 \) and \( n=2 \) the the next day at \( 6am \) both aliens would wait for the other to leave, and when they don't, 
they would both realise that there must be two blue eared aliens and leave at \( 6am \) the day after.

If \( k=k_i \) and  \( n=n_i \) blue eared aliens, then each blue eared alien would see \( n_i-1 \) 
blue eared aliens. And following from the prvious two examples, they would all wait until \( 6am \)
on the \( n_i^{th}-1 \) day, and when they don't see any of the other blue eared ailiens leave, they would all 
simutaneously realise that there must be \( n_i \) blue eared aliens and leave at \( 6am \) the next day.



\end{question}

\begin{question}

\qpart

Let \( k \) be the total number of aliens on the planetoid, and \( n \) the number of aliens with blue ears.

We will prove by induction on \( n \) that all \( n \) blue-eared aliens will leave at 6am on the \( n^\text{th} \) day.

\textbf{Base case:} \( n = 1 \).  
A single blue-eared alien sees no others with blue ears. Knowing that at least one blue-eared alien exists, they conclude it must be themself and leave at 6am the next day. ✓

\textbf{Inductive step:}  
Assume that for some \( n = m \), if there are \( m \) blue-eared aliens, they all leave on the \( m^\text{th} \) day.

Now consider the case \( n = m + 1 \).  
Each blue-eared alien sees \( m \) others with blue ears. They reason:  
“If I do not have blue ears, there are \( m \) blue-eared aliens, and they will all leave on day \( m \).”

When no one leaves on day \( m \), each realises that their assumption must be false, and therefore they too must have blue ears.  
Thus, all \( m + 1 \) blue-eared aliens leave at 6am on the \( (m + 1)^\text{th} \) day.

\textbf{Therefore, by induction}, for any \( n \ge 1 \), all blue-eared aliens leave at 6am on the \( n^\text{th} \) day.

\end{question}


\end{document}